CQM Practical: MBQC in Quantomatic

### 2012-03-06 docs/cqm_practical/cqm_practical.tex
fixed problem w practical sheet

\begin{verbatim}
  $ cd /path/to/quantomatic/
  $ ant run.gui
\end{verbatim}

@@

\begin{enumerate}
  \item A rule that merges adjacent dots of the same colour.
  \item A rule that removes self-loops.
  \item A rule that turns spiders with 1 input and 1 output
\end{enumerate}

@@

\medskip
\noindent{\color{blue} Use the translation from section~\ref{sec:mbqc} to translate this program into a graph in Quantomatic, for measurement outcomes $\{ M_2^0 \rightarrow 0, M_4^0 \rightarrow 0 \}$. Implement enough rules from section~\ref{sec:zx} to normalise the measurement pattern into (\ref{eq:cnot}).}
\medskip

>>>>

\begin{verbatim}
  $ /usr/local/practicals/cqm/quantomatic
\end{verbatim}

@@

\begin{enumerate}
  \item A rule that merges adjacent dots of the same colour.
  \item A rule that removes self-loops.
  \item A rule that turns spiders with 1 input and 1 output into identities.
\end{enumerate}

@@

\[ M_2^0 M_3^0 E_{1,3} E_{2,3} E_{3,4} N_3 N_4 \]

\medskip
\noindent{\color{blue} Use the translation from section~\ref{sec:mbqc} to translate this program into a graph in Quantomatic, for measurement outcomes $\{ M_2^0 \rightarrow 0, M_3^0 \rightarrow 0 \}$. Implement enough rules from section~\ref{sec:zx} to normalise the measurement pattern into (\ref{eq:cnot}).}
\medskip
